\documentclass[nooutcomes]{ximera}

\input{../preamble.tex}

%\prerequisites{algebra}
%\outcomes{arithmeticMean,geometricMean,harmonicMean}

\title{Pythagorean means}

\begin{document}
\begin{abstract}
In this activity we explore the three different means of the
  ancient Greeks.
\end{abstract}
\maketitle


\subsection*{The arithmetic mean}

The \textit{arithmetic mean} is the good-old mean that we are all
familiar with.

\begin{question}
What is the mean that we are all familiar with? Explain how to compute
the mean of $a_1,a_2,\dots,a_n$. Give some examples.
\end{question}

\subsection*{The geometric mean}

The \textit{geometric mean} is a bit different. The geometric mean of $a_1,a_2,\dots, a_n$ is given by:
\[
\left(\prod_{i=1}^n a_i\right)^{1/n}
\]

\begin{question}
Explain an analogy between the arithmetic mean and the geometric mean.
\end{question}

\begin{question}
Can you explain the geometric mean in terms of geometry? First do it
for 2 numbers. Next do it for three.
\end{question}

\subsection*{The harmonic mean}

The \textit{harmonic mean} might be the most mysterious of all. The
harmonic mean of $a_1,a_2,\dots, a_n$ is given by:
\[
\frac{n}{\sum_{i=1}^n \frac{1}{a_i}}
\]

\begin{exploration}
Can you find a connection between the harmonic mean and music?
\end{exploration}


\begin{question}
In the United States, the fuel efficiency of a car is usually given in
the units:
\[
\frac{\text{miles}}{\text{gallon}}
\]
However, in Europe, the fuel efficiency of a car is usually given in
the units:
\[
\frac{\text{liters}}{100 \mathrm{km}}
\]
Give some examples of fuel efficiency (both efficient and
inefficient) with each set of units.
\end{question}


\begin{question}
Now suppose that a car gets $60\frac{\text{miles}}{\text{gallon}}$ and
another car gets $20\frac{\text{miles}}{\text{gallon}}$. What is the
average fuel efficiency?
\end{question}


\begin{question}
Now suppose that a car gets $4\frac{\text{liters}}{100 \mathrm{km}} $
and another car gets $20\frac{\text{liters}}{100 \mathrm{km}}$. What
is the average fuel efficiency?
\end{question}


\begin{exploration}
Compare your answers to the last two questions. Something fishy is
going on, what is it?
\end{exploration}
\end{document}
