\documentclass[nooutcomes]{ximera}

\title{The Beginning of the Modern Era}

\begin{document}
\begin{abstract}
    
\end{abstract}
\maketitle

Our final reading associated with Chapter 5 helped bridge the gap in years between Heron and Cardano by looking more closely at Arabic mathematics and mathematicians.  Europeans were also doing some mathematics during this period, and one of the most famous such is Fibonacci.  Much of the foundation for the mathematics that was developed in Europe starting in the 1500s and 1600s was laid by merchants and other such professionals in the 1200s through the 1400s.  These people, including Fibonacci, helped to bring knowledge from the intellectual center of the world in the Middle East to Europe.


\section{Readings}
First reading: Dunham, Chapter 6, pages 133 - 142

Second reading: \link[Fibonacci Biography]{http://www-history.mcs.st-andrews.ac.uk/Biographies/Fibonacci.html}



\section{Questions}

\begin{question}
Fibonacci defines the concept of a congruum, and then proves that such a number must be divisible by $\answer[given]{24}$.
\end{question}

\begin{question}
In what context were the Fibonacci numbers introduced?
\begin{multipleChoice}
\choice{In a problem about a spider climbing the wall.}
\choice {In a problem about a ship's voyages.}
\choice [correct]{In a problem about rabbit breeding.}
\choice {Without any context; simply a list of numbers.}
\end{multipleChoice}
\end{question}


\begin{question}
What are the most important points from this reading?
\begin{freeResponse}
\end{freeResponse}

\end{question}




\end{document}
