\documentclass[nooutcomes]{ximera}
\input{../preamble}

\title{Mathematicians after Archimedes}

\begin{document}
\begin{abstract}
    
\end{abstract}
\maketitle

Archimedes was certainly a mathematical genius, and following in his footsteps would certainly have been challenging.  Our subject now is these mathematicians, living in changing times.  It is relatively fitting to the story of mathematics that Archimedes was killed by the Romans, as the Roman takeover of much of the Greek world changed the way that people thought about and did mathematics for many years.

Included with the readings are some names of mathematicians whose contributions we will discuss at least briefly in class and in our readings.  By the end of our time on this chapter, you should be able to say a few words about what each person did.
%\begin{itemize}
%\item Eratosthenes 
%\item Apollonius
%\item Heron 
%\item Ptolemy (Look for him in the second reading!)
%\item Hypatia (Listen for her in the video!)
%\item Diophantus
%\end{itemize}




\section{Readings}
First reading: {\bf Eratosthenes, Apollonius, and Heron:} Dunham, Chapter 5, pages 113 - 121 


Second reading: {\bf Ptolemy:} \link[Episodes from the Early History of Mathematics]{https://library.ohio-state.edu/record=b9243572~S7}
\begin{itemize}
	\item Read Chapter 4, Sections 4.1 and 4.2 (pages 101-111).
\end{itemize}

Third reading (short video): {\bf Hypatia:} \link[The Language of the Universe: Mathematics in Ancient Times]{http://library.ohio-state.edu/record=b7179127~S7} 

\begin{itemize}
\item Watch Section 15: End Times of Greek Mathematics
\end{itemize}

Fourth reading: {\bf Diophantus:} \link[Diophantus]{http://www.storyofmathematics.com/hellenistic_diophantus.html}

\section{Questions}

\begin{question}
According to the epitaph riddle, how old was Diophantus when he died? $\answer[given]{84}$
\end{question}

\begin{question}
How is Hypatia primarily remembered today?
\begin{multipleChoice}
\choice{As a mathematician.}
\choice {As a teacher.}
\choice {As a Christian.}
\choice [correct]{As a martyr.}
\end{multipleChoice}
\end{question}


%\begin{question}
%What are the most important points from this reading?
%\begin{freeResponse}
%\end{freeResponse}
%
%\end{question}




\end{document}
