\documentclass[nooutcomes]{ximera}
\input{../preamble}

\title{Newton and Leibniz}

\begin{document}
\begin{abstract}
    
\end{abstract}
\maketitle

The first part of Chapter 8 details an unfortunate phase in the history of mathematics: the debate over who actually ``invented'' calculus.  Part of the first reading will tell the story of this debate, while the second reading gives an overarching history of the development of calculus.  There is a PDF on Carmen titled ``Newton and Leibniz: The Calculus Controversy" which gives a nice overview of all of these ideas, as well as examples of work from both Newton and Leibniz. If you are curious to know more details, the book \link[The Historical Development of the Calculus]{https://library.ohio-state.edu/record=b8693479~S7} has a chapter each on Newton's viewpoint and Leibniz' viewpoint.




\section{Readings}
First reading: Dunham, Chapter 8, pages 184 - 196

Second reading: \link[A History of the Calculus]{https://mathshistory.st-andrews.ac.uk/HistTopics/The_rise_of_calculus/}


\section{Questions}

\begin{question}
How many works of Newton does the article mention which were not published at the time they were written?
$\answer[given]{4}$
\end{question}

\begin{question}
What was the major source of the controversy over calculus?
\begin{multipleChoice}
\choice{No one wrote down their ideas.}
\choice [correct]{The timing of publication.}
\choice {No one read the first publication.}
\choice {It was a popularity contest.}
\end{multipleChoice}
\end{question}


%\begin{question}
%What are the most important points from this reading?
%\begin{freeResponse}
%\end{freeResponse}
%
%\end{question}




\end{document}
