\documentclass{ximera}

\input{../preamble.tex}

\title{The Pythagorean Theorem}

\begin{document}
\begin{abstract}
In this activity we will prove the most famous theorem of
  all.
\end{abstract}
\maketitle



\begin{question}
Remind us, what is the most famous theorem of all and what exactly
does it assert?
\end{question}


\subsection{Euclid's proof}


\begin{question} 
What would one need to prove about the following diagram to prove the
Pythagorean Theorem?
\begin{image}
\begin{tikzpicture}%[alt={Squares drawn on the edges of right triangle ABC.}]
\draw[very thick] (0,0) -- (5,0)--(1.8, 2.4) -- (0,0);
\draw[thick] (0,0) rectangle (5,-5);
\draw[thick] (0,0) -- (-2.4, 1.8) -- (-0.6, 4.2) -- (1.8, 2.4)--(0,0);
\draw[thick] (5,0) --(1.8, 2.4)-- (4.2, 5.6) -- (7.4 , 3.2) -- (5,0);

\node[below left] at (0,0) {$A$};
\node[below right] at (5,0) {$B$};
\node[above] at (1.8, 2.4) {$C$};

\node[left] at (0,-5) {$A''$};
\node[right] at (5,-5) {$B''$};

\node[above] at (4.2, 5.6) {$C''$};
\node[right] at (7.4, 3.2) {$B'$};

\node[above] at (-0.6, 4.2) {$C'$};
\node[left] at (-2.4, 1.8) {$A'$};
\end{tikzpicture}
\end{image}
\end{question}

Let's see if we can do this!


\begin{question}
Draw a line perpendicular to $\overline{AB}$ that passes though both $C$
and $\overline{A'' B''}$. Call the intersection between this line and
$\overline{AB}$, point $E$; call the intersection point between this line
and $\overline{A''B''}$, point $E'$. Explain why $\tri ACA''$ has half the
area of rectangle $AEE'A''$.
\end{question}

\begin{question}
Explain why $\tri ABA'$ has half the area of square $ACC'A'$.
\end{question}

\begin{question}
Explain why $\tri ACA''$ is congruent to $\tri ABA'$. 
\end{question}

\begin{question}
Explain why area of square $ACC'A'$ is equal to the area of rectangle
$AEE'A''$.
\end{question}


\begin{question}
Use similar ideas to complete a proof the Pythagorean Theorem.
\end{question}


\subsection{The converse}

\begin{question} What is the converse to the Pythagorean Theorem? Is it true? How do you prove it?
\end{question}
\end{document}
