\documentclass[nooutcomes]{ximera}
\input{../preamble}

\title{Fermat's Last Theorem}

\begin{document}
\begin{abstract}
    
\end{abstract}
\maketitle

As we consider the Great Theorem of this chapter in our first reading,
we'll also talk a bit more about one of the mathematicians we have
mentioned a few times this semester: Pierre de Fermat.  Dunham discusses 
a little of Fermat's life story as well as Fermat's famous ``Last Theorem'' 
in the first part of Chapter 7. Dunham's text, however, is outdated on 
this subject: Fermat's Last Theorem has in fact been proven!  Our second
reading does a good job of explaining the basic ideas of the theorem
and the history of its proof.

The article in the second reading is still a little older than I'd like, 
however!  Here is a bit more information to bring our story into the present.
\begin{itemize}
	\item Since the article above was published pretty close to
          the publication of Wiles' proof, it ends with some
          uncertainty about the proof.  That uncertainty has been
          removed - the proof has been reviewed and accepted.
	\item Wiles has since won a number of awards for his proof.  Most recently, in 2016 he received the \link[Abel Prize]{http://www.abelprize.no/} in Mathematics.  
	\item Wiles originally gave the proof in about three lectures; now 
	there are instances of entire courses being devoted to the matter.  
	If you're interested in seeing more details for the proof, you can read 
	\link[a very short summary]{https://www.math.wisc.edu/~boston/boston1.pdf}, 
	\link[a medium length summary]{https://www.maa.org/sites/default/files/pdf/upload_library/22/Ford/Gouvea203-222.pdf} 
	or \link[an entire textbook]{https://www.math.wisc.edu/~boston/869.pdf}.  
	You will likely need to have had a significant algebra course to understand much of the proof.
	\item The \link[Wikipedia page]{https://en.wikipedia.org/wiki/Fermat's_Last_Theorem} for Fermat's Last Theorem is heavily referenced and also not a bad place to get general information about the theorem.  (I know, I said you have to be careful with Wikipedia!  Be sure to double-check the information in a non-open-source location.)
\end{itemize}

\section{Readings}
First reading: Dunham, Chapter 7, pages 174 - 183

Second reading: \link[Fermat's Last Theorem]{http://www-history.mcs.st-andrews.ac.uk/HistTopics/Fermat's_last_theorem.html}



\section{Questions}

\begin{question}
Into how many cases did Sophie Germain divide the problem? $\answer[given]{2}$
\end{question}

\begin{question}
Where was Wiles working when he solved Fermat's Last Theorem?
\begin{multipleChoice}
\choice{Stanford.}
\choice [correct]{Princeton.}
\choice {Cambridge.}
\choice {Oxford.}
\end{multipleChoice}
\end{question}

%
%\begin{question}
%What are the most important points from this reading?
%\begin{freeResponse}
%\end{freeResponse}
%
%\end{question}


 %\link[a relatively short summary]{http://math.stanford.edu/~lekheng/flt/gouvea.pdf},

\end{document}
